### 2012-09-04 sections/introduction.tex
Rewrote the "usage scenarios" paragraph
 * added references to surveys given by the professor
 * removed old version

The wide applicability of this approach is easily seen from the pervasive use
of flow records for a vibrant set of network analysis applications. For
instance, the authors in \cite{mkim:2004} use the flow characteristics in the
traffic pattern to formalize a detection function that maps traffic patterns
to different DoS attacks, whereas in \cite{sdominik:2010}, the authors
use the flow-record data to exploit timing characteristics of webmail clients
to classify features that could identify webmail traffic from any other
traffic running over HTTPS.

>>>>

%The wide applicability of this approach is easily seen from the pervasive use
%of flow records for a vibrant set of network analysis applications. For
%instance, the authors in \cite{mkim:2004} use the flow characteristics in the
%traffic pattern to formalize a detection function that maps traffic patterns
%to different DoS attacks, whereas in \cite{sdominik:2010}, the authors
%use the flow-record data to exploit timing characteristics of webmail clients
%to classify features that could identify webmail traffic from any other
%traffic running over HTTPS.

A survey by Sperotto \textit{et al.} \cite{sperotto:2010} gives an overview of
how network flow analysis can be used to detect Denial of Service attacks,
scans probing target systems and the target discovery phase of worms. In
addition, a survey by Callado \textit{et al.} \cite{callado:2009} also lists
behaviour analysis of Internet backbone traffic and general anomaly detection.
